Word Sense Disambiguation\\ \small{Leveraging the NLTK Toolkit and External Tools}

### 2011-04-14 paper/paper.tex
confidence info
Collocation Window graph elaborated...

Collocation window of size 2--4 had the best performance (figure \ref{fig2}), so we looked more closely at those.

>>>>

Collocation window of size 2--4 had the best performance (figure
\ref{fig2}), so we looked more closely at those. What this seems to
imply is that words very close to the head word are the most
important, as expected.
